Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-19 pkg/disttree/inst/draft/rejoinder2.Rnw
final revision and formatting
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2471 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 30a154308024c44cf21f9f0809cf599e54fbbba1

Moreover, sampling variability clearly also plays a role as the differences from Figure~8
are somewhat evened out in the cross-validation, specifically for some of the East Tyrolian 
stations. This is shown in Supplement~B and was already discussed in the corresponding
paragraph in Section~4 (Axams vs.\ other meteorological stations). Additionally, we now
include some comments on this at the end of Section~3.4 where this was admittedly lacking
in the previous version of the manuscript.

@@

>>>>

Moreover, sampling variability clearly also plays a role as the differences from Figure~8
are somewhat evened out in the cross-validation, specifically for some of the East Tyrolean 
stations. This is shown in Supplement~B and was already discussed in the corresponding
paragraph in Section~4 (Axams vs.\ other meteorological stations). Additionally, we now
include some comments on this at the end of Section~3.4 where this was admittedly lacking
in the previous version of the manuscript.

@@

In a predictive setup like the precipitation forecasting the uncertainty of the estimates is not 
of so much concern. Also, the uncertainty due to variation in the response is typically much larger.
